---
title: "DNA presentation"
author: "Allison Davis"
date: "May 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages needed:
seqinR, ape, fields


```{r}
library(seqinr)
```

Sequences we are choosing for today:

American bullfrog (*Rana catesbiana*)
accession: AY324231

Zebrafish (*Danio rerio*)
accession: NM_001083123

Can get sequence data from the NCBI website manually.

Load fasta file to R.

```{r}
library(curl)
dr <- curl("https://raw.githubusercontent.com/celeslie/DNA-Presentation/master/daniorerioAR.fasta")
DRseq <- read.fasta(dr)

rc <- curl("https://raw.githubusercontent.com/celeslie/DNA-Presentation/master/ranacatesbianaAR.fasta")
RCseq <- read.fasta(rc)
```


Take out first line, so that all that is left is a vector containing the nucleotide sequence. 
#what else does the fasta inlcude?

```{r}
DRseq <- DRseq[[1]]
RCseq <- RCseq[[1]]

```

Let's look at what we have.


```{r}
head(DRseq)
head(RCseq)
  # many manipulation functions require a single vector of individual characters.
```